### 2016-06-29 publications/Journal/4b-hotswap.tex
Shorter title for section
Don't just iterate over figures

%TODO explain hotswapping
%TODO why hotswapping
Simply because a synchronization protocol is ideal at the start of the simulation, does not mean that it will still be ideal during the simulation.
It has been frequently shown, and repeated in the previous section, that model behaviour significantly influences the ideal synchronization protocol.
Contrary to many modelling formalisms, the DEVS formalisms makes it possible to model basically any kind of discrete event model.
As such, it is possible for the model to significantly change its behaviour throughout the simulation.

@@

\subsubsection{Visualization of Communication}
To provide some more insight in the models we used as benchmarks previously, we created a simple visualization of the simulation trace.
This trace visualizes the allocation of the model and all defined connections.
For each connection, the number of events transferred is annotated.
Examples are shown for the three benchmark models used before: Figures~\ref{fig:Queue_allocation},~\ref{fig:interconnect_allocation_parallel}, and~\ref{fig:phold_allocation} shows traces for the Queue, Interconnect, and PHOLD models respectively.

>>>>

Simply because a synchronization protocol is ideal at the start of the simulation, does not mean that it will still be ideal during the simulation.
It has been frequently shown, and repeated in the previous section, that model behaviour significantly influences the ideal synchronization protocol.
Contrary to many modelling formalisms, the DEVS formalisms makes it possible to model basically any kind of discrete event model.
As such, it is possible for the model to significantly change its behaviour throughout the simulation.

@@

\subsubsection{Visualization of Communication}
To provide some more insight in the models we used as benchmarks previously, we created a simple visualization of the simulation trace.
This trace visualizes the allocation of the model and all defined connections.
For each connection, the number of events transferred is annotated.
Examples are shown for the three benchmark models used before: Figure~\ref{fig:Queue_allocation}, Figure~\ref{fig:interconnect_allocation_parallel}, and Figure~\ref{fig:phold_allocation} show traces for the Queue, Interconnect, and PHOLD models respectively.
